Analysis for Project

### 2021-11-11 analysis/analysis.Rmd
Move plotting functions to useful functions

```{r}
plot_effect_scatter <- function(model) {

  coefs <- tidy(model) %>%
    filter(str_detect(term, "race") & !str_detect(term, "Multiracial")) %>%
    mutate(term=str_remove(term, "race")) %>%
    select(term, estimate, std.error) %>%
    bind_rows(tibble(term="White", estimate=0, std.error=NA)) %>%
    mutate(multiracial=str_detect(term, "/"))

  #ok convert this to have single race groups for each multiracial group
  #panel and get the assumed midpoint value
  coef_table <- map(as.list(str_subset(coefs$term, "/")), function(x) {
    coefs %>%
      filter(term %in% c(x, str_split(x, "/")[[1]])) %>%
      mutate(mrace=factor(x,
                          levels=c("Black/White","White/Indigenous",
                                   "Black/Indigenous",
                                   "White/Latino","Black/Latino",
                                   "Indigenous/Latino",
                                   "White/Asian","Black/Asian",
                                   "Indigenous/Asian","Latino/Asian")),
             estimate_mid=ifelse(multiracial, 
                                 mean(estimate[!multiracial]),
                                 estimate),
             estimate=ifelse(multiracial, estimate_mid+estimate,
                             estimate))
  }) %>%
    bind_rows()

  ggplot(coef_table, aes(x=estimate_mid, y=estimate,
                         color=multiracial,
                         ymin=estimate-1.96*std.error,
                         ymax=estimate+1.96*std.error))+
    geom_abline(intercept = 0, slope=1, linetype=1, color="grey80")+
    geom_hline(data=subset(coef_table, !multiracial),
               aes(yintercept=estimate), linetype=3, color="grey80")+
    geom_linerange(alpha=0.5)+
    geom_point()+
    geom_text_repel(aes(label=term), size=3)+
    facet_wrap(~mrace, ncol=3)+
    theme_bw()+
    theme(legend.position = "none", panel.grid = element_blank())+
    scale_color_manual(values=c("grey40","black"))+
    labs(x="expected log odds ratio of grade retention based on midpoint",
         y="actual log odds ratio of grade retenion")
}
```

@@

>>>>

```{r}

```

@@

```{r}

```

```{r}
plot_effect_point(model4)
```
